Classical simulation of error correction in a Fibonacci anyon code

### 2014-12-03 fib2.tex
Touched up the abstract a bit.

% This line sets the project root file.
% 
% !TEX root = fib2.tex
% 
%------------------------------------------------------------------------------------------------------------%
\documentclass[a4paper,nofootinbib,superscriptaddress]{revtex4}

@@

\author{Simon Burton}
\affiliation{Centre for Engineered Quantum Systems, School of Physics, The University of Sydney, Sydney, Australia}
\author{Courtney G.\ Brell}
\affiliation{Institut f\"ur Theoretische Physik, Leibniz Universit\"at Hannover, Appelstra\ss e 2, 30167 Hannover, Germany}
\author{Steven T.\ Flammia}
\affiliation{Centre for Engineered Quantum Systems, School of Physics, The University of Sydney, Sydney, Australia}

@@

\begin{abstract}
We study two dimensional systems that support Fibonacci anyon excitations. In general, the braiding of Fibonacci anyons is sufficient for universal quantum computation, and so the classical simulation of their dynamics is likely to be hard. However, we show that for typical processes of interest for the study of successful error-correction in anyon systems, the relevant dynamics are in fact efficiently classically simulable, and make use of this fact to demonstrate the success of an error-correction protocol for a Fibonacci anyon computer. \cggb{Is this claim too bold?} We numerically simulate a phenomenological model of the system and noise processes on lattice sizes up to $128\times128$ sites, and demonstrate an error-correction threshold of around $0.125$ - comparable to those previously known for abelian and (non-universal) non-abelian anyon models.
\end{abstract}

@@

%\vspace{-1.5cm}
% new page after abstract & TOC
%\clearpage
%\tableofcontents
%\clearpage

>>>>

% This line sets the project root file.
% 
% !TEX root = fib2.tex
% 
%------------------------------------------------------------------------------------------------------------%
\documentclass[aps, pra, a4paper, 11pt, nofootinbib, superscriptaddress, tightenlines, 
notitlepage, longbibliography]{revtex4}

@@

\author{Simon Burton}
\affiliation{Centre for Engineered Quantum Systems, School of Physics, 
The University of Sydney, Sydney, Australia}
\author{Courtney G.\ Brell}
\affiliation{Institut f\"{u}r Theoretische Physik, Leibniz Universit\"{a}t Hannover, 
Appelstra\ss{}e 2, 30167 Hannover, Germany}
\author{Steven T.\ Flammia}
\affiliation{Centre for Engineered Quantum Systems, School of Physics, 
The University of Sydney, Sydney, Australia}

@@

\begin{abstract}
We study two-dimensional systems that support Fibonacci anyon excitations. In general, the 
braiding of Fibonacci anyons is sufficient for universal quantum computation, and so the 
classical simulation of their dynamics is likely to be hard. However, we show that for typical 
processes of interest for the study of quantum error correction in anyon systems the 
relevant dynamics can in fact be efficiently simulated classically for a wide range of system 
parameters. We make use of this fact to demonstrate the success of an error-correction 
protocol for a Fibonacci anyon quantum memory below a particular noise threshold. We 
numerically simulate a phenomenological model of the system and noise processes on lattice 
sizes of up to $128\times128$ sites, and demonstrate an error-correction threshold of around 
$12.5\%$, a number that is comparable to those previously known for abelian and 
(non-universal) non-abelian anyon models.
\end{abstract}

@@
